---
title: Access to Justice for All People? An Investigation of the Factors Driving the
  Distribution of Civil Legal Aid Grants
author:
  name: Joanna Schroeder, William & Mary
output: posterdown::posterdown_html
permalink: /civil-legal-aid-poster/
---
<style>
.section h4 {
    break-before: column;
    }
</style>

```{r message = FALSE, warning = FALSE, results = FALSE, include = FALSE}
library(glmnet)
library(foreach)
library(pROC)
library(ggplot2)
library(ggfortify)
library(ggpubr)
library(gridExtra)
library(stargazer)
library(dplyr)
library(grid)
library(gganimate)
library(gifski)
library(png)

dataset <- read.csv(file="/cloud/project/final.einswithindicators.csv")

dataset <- dataset %>% mutate(org_revenue = log(org_revenu), amt_grants_log = log(amt_grants), RURALPOP10PER = (RURALPOP10/TOTPOP10)*100, MINORITYPOP10PER = (MINORITY10/TOTPOP10)*100)

dataset.scale <- dataset %>% mutate_each(funs(scale(.) %>% as.vector), vars = c("org_revenue", "CJS_house", "CJS_house_", "CJS_senate", "CJS_sena_1", "gov_pres_p", "pop_dens", "HIGHSCHOOL", "FOREI_BORN", "NOT_ENG_HO", "VETERAN", "RENT_UNIT", "FIXBB", "POVERTY", "POVERTY125", "UNDER18", "OVER59", "competition_10", "competition_30", "RURALPOP10PER",  "MINORITYPOP10PER")) %>% rename("ORG_REVENUE" = "org_revenue", "CJS_HOUSE" = "CJS_house", "CJS_HOUSE_RANK" = "CJS_house_", "CJS_SENATE" = "CJS_senate", "CJS_SENATE_RANK" = "CJS_sena_1", "GOV_PRES" = "gov_pres_p", "POP_DENS" = "pop_dens", "COMPETITION10" = "competition_10", "COMPETITION30" = "competition_30", "RURAL" = "RURALPOP10PER", "MINORITY" = "MINORITYPOP10PER", "AMT_GRANTS" = "amt_grants_log", "AMT_LSC_GRANTS" = "amt_LSC_gr", "YEAR" = "year_") %>% select("Latitude", "Longitude", "ein", "YEAR", "org_outlier", "AMT_GRANTS", "LSC", "AMT_LSC_GRANTS", "ORG_REVENUE","COMPETITION10", "COMPETITION30", "CJS_HOUSE", "CJS_HOUSE_RANK", "CJS_SENATE", "CJS_SENATE_RANK", "GOV_PRES", "POP_DENS", "HIGHSCHOOL", "FOREI_BORN", "NOT_ENG_HO", "VETERAN", "RENT_UNIT", "FIXBB", "POVERTY", "POVERTY125", "UNDER18", "OVER59", "RURAL",  "MINORITY")
```


# What is civil legal aid?
Access to civil legal justice in the United States is largely an invisible issue, though it affects approximately 70 percent of low-income households each year. This study is concerned with investigating the political, need-based, and capacity factors that drive the allocation of civil legal aid grants to organizations.

# Background and Introduction

# Literature Review

####

# Data and Methods

# Analysis

``` {r message = FALSE, warning = FALSE, include = FALSE}
d <- dataset.scale %>% filter(org_outlier == FALSE)
attach(d)
f <- AMT_GRANTS ~ ORG_REVENUE + CJS_HOUSE + CJS_HOUSE_RANK + CJS_SENATE + CJS_SENATE_RANK + GOV_PRES + POP_DENS + FIXBB + HIGHSCHOOL +  FOREI_BORN + NOT_ENG_HO + VETERAN + RENT_UNIT + POVERTY + POVERTY125 + UNDER18 + OVER59 + COMPETITION10 + COMPETITION30 + RURAL + MINORITY
y <- d$AMT_GRANTS
X <- model.matrix(f, d)
n <- length(y)

cv1 <- cv.glmnet(X, y, nfold = 100, type.measure = "deviance", paralle = TRUE, alpha = 1)
lassomod <- glmnet(X, y, lambda = cv1$lambda.1se, alpha = 1)
cv1.glmnet.fit <- (cv1$glmnet.fit)
tmp_coeffs <- coef(cv1.glmnet.fit, s = cv1$lambda.1se)
lassotable <- data.frame(name = tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1], coefficient = tmp_coeffs@x)
lassotable[order(-lassotable$coefficient),]

lassoplot <- autoplot(cv1$glmnet.fit, "lambda", label = TRUE, main = "LASSO (alpha = 1)") + ylim(-1,1.5) + theme(legend.position="none") + theme(legend.title = element_text(size=20)) + theme(legend.text = element_text(size = 18)) + geom_vline(mapping = NULL, data = NULL, xintercept = log(cv1$lambda.1se), na.rm = FALSE, show.legend = FALSE)

ani_figure <- lassoplot +
  transition_reveal(Lambda)

write
```


####

# Results

# Discussion

# Conclusion

# References
